---
title: "learnRmd"
author: "Michael Dillon"
date: "December 7, 2018"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

R markdown has three components: `to force the new line, I added 2 spaces at the end`  
1. metadata (between 2 `---` at top of document)  
2. text (of any kind, anywhere)  
3. and code, surrounded by 3 backticks for a code chunk, or a single backtick for inline calculations (2x2=`r 2*2`).  

### Metadata
`note the 3 hashes to make a subheading`

The YAML ("YAML ain't markup language") header is picky about formatting, including indentation. Use examples or go to a reference to solve more complicated problems. (see [bookdown.org](www.bookdown.org) for lots of info)

### Text

Again, this is the stuff you are writing to either document your analyses or discuss them (for example, in a paper).

### Code

Can be r, python, and many others an you can control whether the code shows, the output shows, or both.

## Compile
Using the knit button or Ctrl-Shift-K.  

This renders in a new R session ... a very important point because it means that anything in the console from the previous session is now gone. This is a good thing, related to why you shouldn't save your .Rhistory as it can lead to issues with reproducibility.  

You can also render via the command-line or a script, giving you the ability to have automated report generation but you have to worry about reproducibility in that case.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
